---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/"
)
set.seed(0)
```

# Introduction

The aim of this package is to implement the epidemic lambda-coalescent model.

## Installation

You can install EpiLambda from github with:

```{r gh-installation, eval = FALSE}
devtools::install_github("xavierdidelot/EpiLambda")
```

The package can then be loaded using:
```{r}
library(EpiLambda)
```

## Example

Consider that the offspring distribution is Negative-Binomial with dispersion parameter $r=0.5$.
To simulate the ancestry of a sample of size 20 in a population of size 40:

```{r}
t=new_simtree(n=20,nt=40,r=0.5)
plot(t)
axisPhylo(1)
title(xlab='Generations since present')
```

## More information and getting help

For more detailed examples of how to use EpiLambda, see the vignettes [here](https://github.com/xavierdidelot/EpiLambda/tree/master/vignettes).
See also the help included in the package using the R command
`help(package='EpiLambda')`. 

If you have any problem or question please create an issue [here](https://github.com/xavierdidelot/EpiLambda/issues) 
or get in touch by emailing `xavier.didelot@gmail.com`
