---
title: "EpiLambda usage example"
author: "Xavier Didelot"
date: '`r Sys.Date()`'
output:
  pdf_document: default
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{EpiLambda usage example}
  %\usepackage[utf8]{inputenc}
---

## Simulation under beta-coalescent

To simulate the genealogy of a sample of size 50 under the beta-coalescent with parameter $\alpha=1$:

```{r}
library(EpiLambda,quietly = T)
set.seed(0)
t=beta_simtree(n=50,alpha=1)
plot(t)
axisPhylo(1)
title(xlab='Coalescent time unit')
```

## Inference under beta-coalescent

```{r}
beta_mle(t)
```

## Simulation under omega-coalescent

Consider that the offspring distribution is Negative-Binomial with dispersion parameter $r=0.1$.
To simulate the ancestry of a sample of size 50 in a population of size 100:

```{r}
set.seed(0)
t=omega_simtree(n=50,nt=100,r=0.1)
plot(t)
axisPhylo(1)
title(xlab='Generations since present')
```

## Inference under omega-coalescent

Inference of dispersion parameter only:

```{r}
omega_mle(t,nt=100)
```

Inference of effective population size only:

```{r}
omega_mle(t,r=0.1)
```

Joint inference:

```{r}
omega_mle(t)
```
